Remark on the hypothetical judgment

### 2018-01-04 paper.tex
...

On the contrary, an "admissible rule" $\infer{\JJ_2}{\JJ_1}$ is sensitive to
changes in the state of knowledge, and may cease to be valid if a previously
unknown way to experience $\JJ_1$ is found. Such rules may only be construed as
hypothetical judgments if the acts specified by the meanings of their premises
are sufficiently circumscribed so as to satisfy the monotonicity requirement.

>>>>

On the contrary, a rule $\infer{\JJ_2}{\JJ_1}$ merely expresses the closure of
all mathematical constructions under the inference of $\JJ_2$ from $\JJ_1$;
this kind of closure is sensitive to changes in the state of knowledge, and may
cease to be valid if a previously unknown way to experience $\JJ_1$ is found.
This is the sense in which extra-logical principles like Brouwer's Bar Thesis
and Markov's Principle are ``rules''~\cite{sundholm-mva}. Such rules may only be construed as
hypothetical judgments if the acts specified by the meanings of their premises
are sufficiently circumscribed so as to satisfy the monotonicity requirement.
